Radioastronomical image reconstruction using Kalman filter under ionospheric perturbations

### 2022-08-14 article/article.tex
forgot ctrl s lmao
._.

	\newpage

	\part{Introduction}

	A sensitive part of the filter is the observations model, needing precise knowledge of antennas positions and directions. An objective of this work is to determine how inaccuracies in these measurements affect image reconstruction, and if it is realistically usable in radio astronomical imagery. \\

@@

>>>>

@@

	Research in SATIE is dispatched around two main divisions :

	\begin{tabular}{|c||c|c|} % a traduire ffs
		\hline
		Divisions & Components and Systems for electrical energy & Multi-scale information and analysis systems \\ & (CSEE) & (SIAME) \\\hline
		Research fields & \begin{tabular}{@{}c@{}}
			Materials: from synthesis to application\vspace{8px} \\ Power electronics: integration, \\ usage constraints, interfaces\vspace{8px} \\ Transducers and energy systems: \\ methodologies, design and control
		\end{tabular} & \begin{tabular}{@{}c@{}}
			Instrumentation and imagery\vspace{5px} \\ Methods and tools for signals and systems\\ (MOSS)
		\end{tabular}
		\\\hline
	\end{tabular}
	\vspace{7px}\\
	I did my internship in the SIAME/MOSS division. \\
	The SIAME/MOSS division is focused on getting a better understanding and mastering complex systems. The three main topics of the division are :
	\paragraph{Data and image analysis:} this topic's main goal is to estimate physical or semantic quantities from observations data. This data is incomplete, inaccurate, and not absolutely reliable. When data is generated using multi-sensor systems, it presents similarities and complementarities that can be used to get better estimations.

	\newpage
	\part{Introduction}

	A sensitive part of the filter is the observations model, needing precise knowledge of antennas positions and directions. A of this goal work is to determine how inaccuracies in these measurements affect image reconstruction, and if it is realistically usable in radio astronomical imagery. \\
